### 2018-02-13 thermoelectricity/paper.tex
All plots

	\papereq{OhmicHeating}{P = I ^ 2 R}{\textbf{TODO}}
	\begin{paperwhere}
		\papervar{P}{heat production per unit time}{\watt}
		\papervar{I}{current}{\ampere}
		\papervar{R}{resistance}{\ohm}
	\end{paperwhere}

@@

	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but are too small to be visible.}

	To visualize the results for the

>>>>

	\papereq{OhmicHeating}{P = I ^ 2 R}{AF, 2014}
	\begin{paperwhere}
		\papervar{P}{heat production per unit time}{\watt}
		\papervar{I}{current}{\ampere}
		\papervar{R}{resistance}{\ohm}
	\end{paperwhere}

@@

	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible.}

	To visualize the results for the fixed current setup supplied by the built-in power supply, temperature difference and the electrical power input were plotted against time. All uncertainties were propagates using the method of quadratures.

	\paperfig{part2a}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible.}

	To visualize the results for various power inputs supplied by the Variac transformer, reservoir temperatures, power, and the Seebeck voltage were plotted versus the input power. All uncertainties were propagates using the method of quadratures.

	\paperfig{part2b}{\pdf{part2b-data}}{Temperature vs. input power (left), total electrical power vs. input power (middle) and total voltage across the TEC vs. input power (right). Uncertainties were included but were too small to be visible.}
